NFC and burnout in teachers - A replication and extension study

### 2022-03-04 Manuscript/Manuscript.tex
changed keywords and reference style

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={NFC and burnout in teachers - A replication and extension study},
  pdfauthor={Josephine Zerna1, Nicole Engelmann2, Anja Strobel3, \& Alexander Strobel1},
  pdflang={en-EN},
  pdfkeywords={mediation, resources, demands, structural equation modelling, Covid-19},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{NFC and burnout in teachers}
\keywords{mediation, resources, demands, structural equation modelling, Covid-19\newline\indent Word count: ~ 5600}
\usepackage{lineno}

@@

Need for Cognition (NFC) is a stable intrinsic motivation to seek out and especially to enjoy effortful cognitive activities (Cacioppo \& Petty, 1982).
As it bridges the gap between cognition and motivation, NFC is considered to be an investment trait (Stumm \& Ackerman, 2013), and has come to the fore of psychological research in the last years.
NFC can easily be assessed using the Need for Cognition Scale (NCS), a self-report questionnaire with 18 to 34 items (Cacioppo et al., 1984; Cacioppo \& Petty, 1982; German form: Bless et al., 1994).
While many studies have found medium sized positive associations of NFC with academic performance (Cazan \& Indreica, 2014; Grass et al., 2017; Lavrijsen et al., 2021; Stumm \& Ackerman, 2013; Zheng et al., 2020), recent investigations have also looked at NFC as a personal resource in academic and work contexts.
Individuals high in NFC have more positive emotions at the end of the work day (Rosen et al., 2020), higher work motivation, perceive their roles as less ambiguous (Nowlin et al., 2017), are less likely to drop out of college (Grass et al., 2017; Klaczynski \& Fauth, 1996), and have less anxiety regarding their course work (Karagiannopoulou et al., 2020), with these associations being small to medium sized by and large.
These findings suggest that individuals high in NFC might be less prone to experience adverse effects of work stress, which range from physical (Dragano et al., 2017; Steptoe \& Kivimäki, 2013) to psychological consequences (Madsen et al., 2017; Maslach \& Leiter, 2016; Wiesner et al., 2005).

One of these psychological consequences is burnout, a state of exhaustion and cynicism caused by long-term overstimulation in the workplace, which results in employees being dissatisfied, being sick more often, and performing poorly (Schaufeli \& Salanova, 2014).
Burnout is especially prevalent in social jobs such as healthcare or teaching because the worker is always in conflict between advocating for their client and meeting the goals set by the employer (Gray-Stanley \& Muramatsu, 2011; Lloyd et al., 2002).
Lackritz (2004) found that university teachers' burnout scores were higher the more students they had, the higher their teaching load was, and the more time they spent grading students' work.
Burnout is most often assessed using the Maslach Burnout Inventory (MBI) (Maslach et al., 1997), a self-report questionnaire with three subscales: \emph{Emotional exhaustion}, a sense of fatigue and depletion, \emph{depersonalisation}, a negative attitude towards clients, along with a loss of idealism, and \emph{reduced personal efficacy}, a decline of capability and coping skills.

Individuals with high burnout scores are often passive copers, high in neuroticism, low in self-esteem, and have an external locus of control (Schaufeli \& Salanova, 2014).
NFC on the other hand is negatively associated with those variables (Double \& Birney, 2016; Fleischhauer et al., 2019; Ghorbani et al., 2004; Grass et al., 2018; Osberg, 1987), suggesting that people high in NFC are less prone to experience burnout.
This is supported by findings that NFC showed moderate to large negative associations with burnout scores in adults (Fleischhauer et al., 2019), students (Fleischhauer et al., 2019; Naderi et al., 2018), and teacher trainees (Grass et al., 2018).
However, the associations of NFC with the sum score and the subscales of the MBI are not always consistent between these studies.
This is likely not caused by inaccurate measurement, since the validity of both NCS (Bless et al., 1994; Osberg, 1987; Tolentino et al., 1990) and MBI (Brady et al., 2021; Kantas \& Vassilaki, 1997; Schaufeli et al., 2001; Valdivia Vázquez et al., 2021) has been demonstrated in multiple studies.
What is more likely is the influence of one or more other variables, moderating or mediating the association of NFC and burnout.
Grass et al. (2018) investigated such a mediation and found that the relation of NFC and the MBI subscale reduced personal-efficacy was fully mediated by higher habitual use of reappraisal, more active coping, and less passive coping, but not by habitual use of suppression or self-control.
Reappraisal and suppression are two emotion regulation strategies, which refer to the cognitive reassessment of a stressor and the inhibition of emotional reactions, respectively (Gross, 1998).
The findings by Grass et al. (2018) suggest that individuals high in NFC experience a weaker decline in personal efficacy in response to long-term stress because they actively reassess the situation in a way that reinforces their sense of self-efficacy and don't avoid dealing with the stressor (Strobel et al., 2017).
One goal of this paper was to replicate the findings of Grass et al. (2018) using a multiple mediation model on cross-sectional self-report data of teachers.
We expected NFC to be negatively associated with reduced personal efficacy via higher reappraisal scores, but not via suppression, via self-control, or directly.

Furthermore, we extended the analysis to other possible mediators.
These mediators were motivated by our own recent survey of the literature on NFC and well-being, which suggested that individuals high in NFC might not only have a high level of personal resources but also overestimate their own resources to a certain degree (Zerna et al., 2021).
This can take the form of patients with higher NFC having lower intentions to consult their physician (Latimer et al., 2007) or adults with higher NFC having higher intentions to consume high calorie beverages (Gallivan, 2020) after detailed message interventions designed to promote consultations and healthier beverage choices, respectively.
Only a balance of resources and demands results in personal well-being, while an imbalance threatens well-being, regardless of whether this imbalance is in favour of resources or demands (Dodge et al., 2012).
Following the framework of Hobfoll (1989), resources can be objects with practical or status purpose, conditions like marriage or tenure, personality aspects like coping style, and energies such as time, money, or knowledge.
In the case of NFC, resources are from the categories personality and energies: Personality, because NFC is a trait, encompassing a curious, analytic, and passionate approach to challenges, and energies, because individuals high in NFC have been coping actively all their life, which enriches their level of experience and knowledge in approaching challenges (Cacioppo et al., 1996).
These personal resources matter with regard to stress assessment (how the situation is appraised) and with regard to both coping and recovery (Salanova et al., 2006).
We therefore investigated whether the association of NFC and burnout was mediated by different ratios of demands and resources; demands that are too high to be dealt with using one's personal resources (\emph{demands too high}), demands that are too low for one's personal resources (\emph{demands too low}), and a balanced fit of demands and resources (\emph{demand-resource-fit}).
Using the same data as for the replication, we computed a structural equation model (SEM) to assess the influence of these mediators.
Since individuals high in NFC are confident in their abilities (Bye \& Pushkar, 2009; Ghorbani et al., 2004; Heppner et al., 1983; Klaczynski \& Fauth, 1996), we expected NFC to be negatively associated with \emph{demands too high}, and positively associated with \emph{demands too low} and \emph{demand-resource-fit}.
And since burnout results from constant unpleasant activation by high demands, we expected it to be positively associated with \emph{demands too high} and negatively associated with \emph{demand-resource-fit}.
However, we had no hypothesis regarding the association of \emph{demands too low} and burnout, because even though \emph{demands too low} is akin to the concept of boredom and the consequences of boredom and burnout are very similar, burnout is a state with even lower activation and even more negative affect than boredom (Schaufeli \& Salanova, 2014).
It has already been shown that the Covid-19 pandemic has exacerbated the rising prevalence of burnout (Fröbe \& Franco, 2021), so we incorporated the degree of feeling burdened by the pandemic in an exploratory approach.
To sum up, this study had three aims: Replicating findings of mediation between NFC and burnout, investigating the impact of different demand-resource-ratios on the relationship between NFC and burnout, and exploring the impact of other variables such as perceived burden by the pandemic.

@@

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study (Simmons et al., 2012).
Our preregistration, the data, and the R Markdown document used to analyze the data and write this manuscript, using the R package \emph{papaja} (Aust \& Barth, 2020), are available at \url{https://osf.io/36ep9/}.
The procedure was evaluated and approved by the Ethics Committee of the Chemnitz University of Technology (reference number: V-389-15-AS-Burnout-08062020).
It was not considered to require further ethical approvals and hence, as uncritical concerning ethical aspects according to the criteria used by the Ethics Committee, which includes aspects of the sample of healthy adults, voluntary attendance, noninvasive measures, no deception, and appropriate physical and mental demands on the subject.

@@

All questionnaires were used in their German form.
Burnout was assessed using the 21-item Maslach Burnout Inventory (MBI, Büssing \& Perrar, 1992), with items such as ``I don't really care what happens to some recipients'' and responses on a 7-point Likert scale from 0 (never) to 6 (every day).
Its subscales \emph{emotional exhaustion}, \emph{depersonalization}, and \emph{reduced personal efficacy} showed acceptable internal consistency (Cronbach's \(\alpha>.70\)) and low retest reliabilities of \(r_{tt}=.60\), \(r_{tt}=.54\), and \(r_{tt}=.57\), respectively, over the span of one year in teachers (Maslach et al., 1997).
NFC was assessed with the 16-item short version of the German NFC scale (NCS) (Bless et al., 1994), consisting of items (e.g., ``Thinking is not my idea of fun,'' recoded) that are answered on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree).
The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\)) (Bless et al., 1994; Fleischhauer et al., 2010) and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks (Fleischhauer et al., 2015).
Self-control was measured using the short form of the German Self-Control Scale {[}SCS-K-D; Bertrams and Dickhäuser (2009){]} that comprises 13 items (e.g., ``I am able to work effectively toward long-term goals'') with a 5-point Likert scale ranging from -2 (completely disagree) to +2 (completely agree), with comparably high reliability (Cronbach's \(\alpha>.80\), 7-week retest reliability \(r_{tt}=.82\)) (Bertrams \& Dickhäuser, 2009).
Reappraisal and suppression was measured using the 10-item Emotion Regulation Questionnaire (ERQ) (Abler \& Kessler, 2009).
The scale has items such as ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (reappraisal) and ``I keep my emotions to myself'' (suppression), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\)) (Preece et al., 2019).
Work satisfaction was assessed using the Allgemeine Arbeitszufriedenheit questionnaire (Fischer \& Lück, 2014) with items such as ``Sometimes I feel like my work doesn't really matter in my firm,'' which are answered on a 5-point Likert scale from 1 to 5 and different anchors depending on the item.
The scale has a split-half reliability of \(r_{tt}=.95\) (Fischer \& Lück, 2014).
Eleven items were created to assess each participant's current burden by the Covid-19 pandemic, such as whether they belong to a risk group or whether they currently had a higher workload.
The translated Covid-19 items can be found in the \emph{Supplementary Material S1}.
Due to a technical error during survey setup, the coping style data of the Erfurter Belastungsinventar (Böhm-Kasper et al., 2001) could not be used, so we could not replicate the mediation of NFC and burnout by active and passive coping.

@@

All items, apart from those making up the demand-resource-ratios, were reverse coded according to the scale manuals.
The latent factor NFC was computed by subjecting the NCS items to a parcelling procedure (Little et al., 2002), a method that is used in SEM when only relations between but not within constructs are of interest.
Principal component analysis was used to determine the factor loadings of each NCS item onto the first component.
Then, the items were randomly divided into four parcels and the average item loading per parcel was computed.
This was repeated 10,000 times to find the parcelling choice with the smallest difference in average item loadings between parcels.
The latent factor MBI was computed using the three subscales as indicators.
For the demand-resource-ratios, we used three items from the work satisfaction scale each.
The latent factor \emph{demands too high} was indicated by items 4, 8, and 9, \emph{demands too low} by the recoded items 12, 26, and 27, and \emph{demand-resource-fit} by items 17, 22, and 24.
The items can be translated as follows: 4) ``There is too much pressure on me.'' 8) ``There is often too much being demanded of us at work.'' 9) ``I often feel tired and weary because of my work.'' 12) ``I can realize my ideas here.'' 17) ``I take pleasure in my work.'' 22) ``Does your place of work give you the opportunity to do what you do best?'' 24) ``Does your place of work give you enough opportunities to use your skills?'' 26) ``Are you happy with your promotion prospects?'' and 27) ``Are you happy with your position when comparing it to your skills?''
Model parameters were estimated using the maximum likelihood method with robust standard errors.
Model fit was evaluated by looking at the Chi-square test statistic, CFI, SRMR, and RMSEA.

@@

Correlations and internal consistencies are displayed in Table 2.
For this descriptive analysis, the variables \emph{demands too high}, \emph{demands too low}, and \emph{demand-resource-fit} were computed as a sum of their item scores, not weighted as in the structural equation model.
Using traditional cut-off values (Nunnally \& Bernstein, 1994), the Cronbach's Alpha of the three demand-resource-ratios can be considered \emph{acceptable}.
The more robust MacDonald's Omega (Dunn et al., 2014) did not deviate much from Cronbach's Alpha and indicated \emph{acceptable} to \emph{good} internal consistency.
As expected, the MBI score showed a large positive correlation with \emph{demands too high} (\(r_s\) = .67, \emph{p} \textless{} .001) and a large negatve one with \emph{demand-resource-fit} (\(r_s\) = -.55, \emph{p} \textless{} .001).
Surprisingly, the correlation between the MBI score and \emph{demands too low} was positive and also large (\(r_s\) = .44, \emph{p} \textless{} .001).
The NFC score correlated negatively with the MBI sum score and about equally with all subscales, contrary to some previous observations in other studies.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Abler2009}{}%
Abler, B., \& Kessler, H. (2009). Emotion {Regulation} {Questionnaire} -- {Eine} deutschsprachige {Fassung} des {ERQ} von {Gross} und {John}. \emph{Diagnostica}, \emph{55}(3), 144--152. \url{https://doi.org/10.1026/0012-1924.55.3.144}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={NFC and burnout in teachers - A replication and extension study},
  pdfauthor={Josephine Zerna1, Nicole Engelmann2, Anja Strobel3, \& Alexander Strobel1},
  pdflang={en-EN},
  pdfkeywords={behaviour, resources, demands, education, Covid-19},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{NFC and burnout in teachers}
\keywords{behaviour, resources, demands, education, Covid-19\newline\indent Word count: ~ 5600}
\usepackage{lineno}

@@

Need for Cognition (NFC) is a stable intrinsic motivation to seek out and especially to enjoy effortful cognitive activities (Cacioppo and Petty, 1982).
As it bridges the gap between cognition and motivation, NFC is considered to be an investment trait (Stumm and Ackerman, 2013), and has come to the fore of psychological research in the last years.
NFC can easily be assessed using the Need for Cognition Scale (NCS), a self-report questionnaire with 18 to 34 items (Cacioppo et al., 1984; Cacioppo and Petty, 1982; German form: Bless et al., 1994).
While many studies have found medium sized positive associations of NFC with academic performance (Cazan and Indreica, 2014; Grass et al., 2017; Lavrijsen et al., 2021; Stumm and Ackerman, 2013; Zheng et al., 2020), recent investigations have also looked at NFC as a personal resource in academic and work contexts.
Individuals high in NFC have more positive emotions at the end of the work day (Rosen et al., 2020), higher work motivation, perceive their roles as less ambiguous (Nowlin et al., 2017), are less likely to drop out of college (Grass et al., 2017; Klaczynski and Fauth, 1996), and have less anxiety regarding their course work (Karagiannopoulou et al., 2020), with these associations being small to medium sized by and large.
These findings suggest that individuals high in NFC might be less prone to experience adverse effects of work stress, which range from physical (Dragano et al., 2017; Steptoe and Kivimäki, 2013) to psychological consequences (Madsen et al., 2017; Maslach and Leiter, 2016; Wiesner et al., 2005).

One of these psychological consequences is burnout, a state of exhaustion and cynicism caused by long-term overstimulation in the workplace, which results in employees being dissatisfied, being sick more often, and performing poorly (Schaufeli and Salanova, 2014).
Burnout is especially prevalent in social jobs such as healthcare or teaching because the worker is always in conflict between advocating for their client and meeting the goals set by the employer (Gray-Stanley and Muramatsu, 2011; Lloyd et al., 2002).
Lackritz (2004) found that university teachers' burnout scores were higher the more students they had, the higher their teaching load was, and the more time they spent grading students' work.
Burnout is most often assessed using the Maslach Burnout Inventory (MBI) (Maslach et al., 1997), a self-report questionnaire with three subscales: \emph{Emotional exhaustion}, a sense of fatigue and depletion, \emph{depersonalisation}, a negative attitude towards clients, along with a loss of idealism, and \emph{reduced personal efficacy}, a decline of capability and coping skills.

Individuals with high burnout scores are often passive copers, high in neuroticism, low in self-esteem, and have an external locus of control (Schaufeli and Salanova, 2014).
NFC on the other hand is negatively associated with those variables (Double and Birney, 2016; Fleischhauer et al., 2019; Ghorbani et al., 2004; Grass et al., 2018; Osberg, 1987), suggesting that people high in NFC are less prone to experience burnout.
This is supported by findings that NFC showed moderate to large negative associations with burnout scores in adults (Fleischhauer et al., 2019), students (Fleischhauer et al., 2019; Naderi et al., 2018), and teacher trainees (Grass et al., 2018).
However, the associations of NFC with the sum score and the subscales of the MBI are not always consistent between these studies.
This is likely not caused by inaccurate measurement, since the validity of both NCS (Bless et al., 1994; Osberg, 1987; Tolentino et al., 1990) and MBI (Brady et al., 2021; Kantas and Vassilaki, 1997; Schaufeli et al., 2001; Valdivia Vázquez et al., 2021) has been demonstrated in multiple studies.
What is more likely is the influence of one or more other variables, moderating or mediating the association of NFC and burnout.
Grass et al. (2018) investigated such a mediation and found that the relation of NFC and the MBI subscale reduced personal-efficacy was fully mediated by higher habitual use of reappraisal, more active coping, and less passive coping, but not by habitual use of suppression or self-control.
Reappraisal and suppression are two emotion regulation strategies, which refer to the cognitive reassessment of a stressor and the inhibition of emotional reactions, respectively (Gross, 1998).
The findings by Grass et al. (2018) suggest that individuals high in NFC experience a weaker decline in personal efficacy in response to long-term stress because they actively reassess the situation in a way that reinforces their sense of self-efficacy and don't avoid dealing with the stressor (Strobel et al., 2017).
One goal of this paper was to replicate the findings of Grass et al. (2018) using a multiple mediation model on cross-sectional self-report data of teachers.
We expected NFC to be negatively associated with reduced personal efficacy via higher reappraisal scores, but not via suppression, via self-control, or directly.

Furthermore, we extended the analysis to other possible mediators.
These mediators were motivated by our own recent survey of the literature on NFC and well-being, which suggested that individuals high in NFC might not only have a high level of personal resources but also overestimate their own resources to a certain degree (Zerna et al., 2021).
This can take the form of patients with higher NFC having lower intentions to consult their physician (Latimer et al., 2007) or adults with higher NFC having higher intentions to consume high calorie beverages (Gallivan, 2020) after detailed message interventions designed to promote consultations and healthier beverage choices, respectively.
Only a balance of resources and demands results in personal well-being, while an imbalance threatens well-being, regardless of whether this imbalance is in favour of resources or demands (Dodge et al., 2012).
Following the framework of Hobfoll (1989), resources can be objects with practical or status purpose, conditions like marriage or tenure, personality aspects like coping style, and energies such as time, money, or knowledge.
In the case of NFC, resources are from the categories personality and energies: Personality, because NFC is a trait, encompassing a curious, analytic, and passionate approach to challenges, and energies, because individuals high in NFC have been coping actively all their life, which enriches their level of experience and knowledge in approaching challenges (Cacioppo et al., 1996).
These personal resources matter with regard to stress assessment (how the situation is appraised) and with regard to both coping and recovery (Salanova et al., 2006).
We therefore investigated whether the association of NFC and burnout was mediated by different ratios of demands and resources; demands that are too high to be dealt with using one's personal resources (\emph{demands too high}), demands that are too low for one's personal resources (\emph{demands too low}), and a balanced fit of demands and resources (\emph{demand-resource-fit}).
Using the same data as for the replication, we computed a structural equation model (SEM) to assess the influence of these mediators.
Since individuals high in NFC are confident in their abilities (Bye and Pushkar, 2009; Ghorbani et al., 2004; Heppner et al., 1983; Klaczynski and Fauth, 1996), we expected NFC to be negatively associated with \emph{demands too high}, and positively associated with \emph{demands too low} and \emph{demand-resource-fit}.
And since burnout results from constant unpleasant activation by high demands, we expected it to be positively associated with \emph{demands too high} and negatively associated with \emph{demand-resource-fit}.
However, we had no hypothesis regarding the association of \emph{demands too low} and burnout, because even though \emph{demands too low} is akin to the concept of boredom and the consequences of boredom and burnout are very similar, burnout is a state with even lower activation and even more negative affect than boredom (Schaufeli and Salanova, 2014).
It has already been shown that the Covid-19 pandemic has exacerbated the rising prevalence of burnout (Fröbe and Franco, 2021), so we incorporated the degree of feeling burdened by the pandemic in an exploratory approach.
To sum up, this study had three aims: Replicating findings of mediation between NFC and burnout, investigating the impact of different demand-resource-ratios on the relationship between NFC and burnout, and exploring the impact of other variables such as perceived burden by the pandemic.

@@

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study (Simmons et al., 2012).
Our preregistration, the data, and the R Markdown document used to analyze the data and write this manuscript, using the R package \emph{papaja} (Aust and Barth, 2020), are available at \url{https://osf.io/36ep9/}.
The procedure was evaluated and approved by the Ethics Committee of the Chemnitz University of Technology (reference number: V-389-15-AS-Burnout-08062020).
It was not considered to require further ethical approvals and hence, as uncritical concerning ethical aspects according to the criteria used by the Ethics Committee, which includes aspects of the sample of healthy adults, voluntary attendance, noninvasive measures, no deception, and appropriate physical and mental demands on the subject.

@@

All questionnaires were used in their German form.
Burnout was assessed using the 21-item Maslach Burnout Inventory (MBI, Büssing and Perrar, 1992), with items such as ``I don't really care what happens to some recipients'' and responses on a 7-point Likert scale from 0 (never) to 6 (every day).
Its subscales \emph{emotional exhaustion}, \emph{depersonalization}, and \emph{reduced personal efficacy} showed acceptable internal consistency (Cronbach's \(\alpha>.70\)) and low retest reliabilities of \(r_{tt}=.60\), \(r_{tt}=.54\), and \(r_{tt}=.57\), respectively, over the span of one year in teachers (Maslach et al., 1997).
NFC was assessed with the 16-item short version of the German NFC scale (NCS) (Bless et al., 1994), consisting of items (e.g., ``Thinking is not my idea of fun'', recoded) that are answered on a 7-point Likert scale ranging from -3 (completely disagree) to +3 (completely agree).
The scale shows comparably high internal consistency (Cronbach's \(\alpha>.80\)) (Bless et al., 1994; Fleischhauer et al., 2010) and a retest reliability of \(r_{tt}=.83\) across 8 to 18 weeks (Fleischhauer et al., 2015).
Self-control was measured using the short form of the German Self-Control Scale {[}SCS-K-D; Bertrams and Dickhäuser (2009){]} that comprises 13 items (e.g., ``I am able to work effectively toward long-term goals'') with a 5-point Likert scale ranging from -2 (completely disagree) to +2 (completely agree), with comparably high reliability (Cronbach's \(\alpha>.80\), 7-week retest reliability \(r_{tt}=.82\)) (Bertrams and Dickhäuser, 2009).
Reappraisal and suppression was measured using the 10-item Emotion Regulation Questionnaire (ERQ) (Abler and Kessler, 2009).
The scale has items such as ``When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm'' (reappraisal) and ``I keep my emotions to myself'' (suppression), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach's \(\alpha>.75\)) (Preece et al., 2019).
Work satisfaction was assessed using the Allgemeine Arbeitszufriedenheit questionnaire (Fischer and Lück, 2014) with items such as ``Sometimes I feel like my work doesn't really matter in my firm'', which are answered on a 5-point Likert scale from 1 to 5 and different anchors depending on the item.
The scale has a split-half reliability of \(r_{tt}=.95\) (Fischer and Lück, 2014).
Eleven items were created to assess each participant's current burden by the Covid-19 pandemic, such as whether they belong to a risk group or whether they currently had a higher workload.
The translated Covid-19 items can be found in the \emph{Supplementary Material S1}.
Due to a technical error during survey setup, the coping style data of the Erfurter Belastungsinventar (Böhm-Kasper et al., 2001) could not be used, so we could not replicate the mediation of NFC and burnout by active and passive coping.

@@

All items, apart from those making up the demand-resource-ratios, were reverse coded according to the scale manuals.
The latent factor NFC was computed by subjecting the NCS items to a parcelling procedure (Little et al., 2002), a method that is used in SEM when only relations between but not within constructs are of interest.
Principal component analysis was used to determine the factor loadings of each NCS item onto the first component.
Then, the items were randomly divided into four parcels and the average item loading per parcel was computed.
This was repeated 10,000 times to find the parcelling choice with the smallest difference in average item loadings between parcels.
The latent factor MBI was computed using the three subscales as indicators.
For the demand-resource-ratios, we used three items from the work satisfaction scale each.
The latent factor \emph{demands too high} was indicated by items 4, 8, and 9, \emph{demands too low} by the recoded items 12, 26, and 27, and \emph{demand-resource-fit} by items 17, 22, and 24.
The items can be translated as follows: 4) ``There is too much pressure on me.'', 8) ``There is often too much being demanded of us at work.'', 9) ``I often feel tired and weary because of my work.'', 12) ``I can realize my ideas here.'', 17) ``I take pleasure in my work.'', 22) ``Does your place of work give you the opportunity to do what you do best?'', 24) ``Does your place of work give you enough opportunities to use your skills?'', 26) ``Are you happy with your promotion prospects?'', and 27) ``Are you happy with your position when comparing it to your skills?''.
Model parameters were estimated using the maximum likelihood method with robust standard errors.
Model fit was evaluated by looking at the Chi-square test statistic, CFI, SRMR, and RMSEA.

@@

Correlations and internal consistencies are displayed in Table 2.
For this descriptive analysis, the variables \emph{demands too high}, \emph{demands too low}, and \emph{demand-resource-fit} were computed as a sum of their item scores, not weighted as in the structural equation model.
Using traditional cut-off values (Nunnally and Bernstein, 1994), the Cronbach's Alpha of the three demand-resource-ratios can be considered \emph{acceptable}.
The more robust MacDonald's Omega (Dunn et al., 2014) did not deviate much from Cronbach's Alpha and indicated \emph{acceptable} to \emph{good} internal consistency.
As expected, the MBI score showed a large positive correlation with \emph{demands too high} (\(r_s\) = .67, \emph{p} \textless{} .001) and a large negatve one with \emph{demand-resource-fit} (\(r_s\) = -.55, \emph{p} \textless{} .001).
Surprisingly, the correlation between the MBI score and \emph{demands too low} was positive and also large (\(r_s\) = .44, \emph{p} \textless{} .001).
The NFC score correlated negatively with the MBI sum score and about equally with all subscales, contrary to some previous observations in other studies.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Abler2009}{}%
Abler B and Kessler H (2009) Emotion {Regulation} {Questionnaire} -- {Eine} deutschsprachige {Fassung} des {ERQ} von {Gross} und {John}. \emph{Diagnostica} 55(3): 144--152. DOI: \href{https://doi.org/10.1026/0012-1924.55.3.144}{10.1026/0012-1924.55.3.144}.

\leavevmode\hypertarget{ref-Aust2020}{}%
Aust F and Barth M (2020) \emph{{papaja}: {Create} {APA} Manuscripts with {R Markdown}}. Available at: \url{https://github.com/crsh/papaja}.

\leavevmode\hypertarget{ref-Bandura1997}{}%
Bandura A (1997) \emph{Self-{Efficacy}: {The} Exercise of Control}. Worth Publishers.
